### 2017-04-20 Paper Drafts/Draft 0/Draft0.tex
Added evolutionary tree figure

The post processed echolocation call data accompanying Stathopoulos et al. \cite{stathopoulos2017bat} was used in this analysis. Echolocation calls were recorded across north and central Mexico with a Pettersson 1000x bat detector (Pettersson Elektronik AB, Uppsala, Sweden). Live trapped bats were measured and identified to species level using field keys.\cite{ceballos2005mamiferos} \cite{medellin2sanchez} Bats were recorded either while released from the hand or while tied to a zip line. The bat detector was set to record calls manually in real time, full spectrum at 500 kHz. 
In total the dataset consists of 22 species in five families, 449 individual bats and 1814 individual echolocation call recordings.

\begin{table}[ht]
	\tbl{Echolocation Call Dataset Statistics}
	{\begin{tabular}{@{}lcc@{}} \toprule
			Species & Individuals & Calls \\ \colrule
			Family: Emballonuridae & & \\
			1 \textit{Balantiopteryx plicata} & 16 & 100 \\
			\\
			Family: Molossidae && \\
			2 \textit{Nyctinomops femorosaccus} & 16 & 100 \\
			3 \textit{Tadarida brasiliensis} & 49 & 100  \\
			\\
			Family: Vespertilionidae && \\
			4 \textit{Antrozous pallidus} & 58 & 100 \\
			5 \textit{Eptesicus fuscus} & 74 & 100 \\
			6 \textit{Idionycteris phyllotis} & 6 & 100 \\
			7 \textit{Lasiurus blossevillii} & 10 & 90 \\
			8 \textit{Lasiurus cinereus} & 5 & 42 \\
			9 \textit{Lasiurus xanthinus} & 8 & 100 \\
			10 \textit{Myotis volans} & 8 & 100 \\
			11 \textit{Myotis yumanensis} & 5 & 89 \\
			12 \textit{Pipistrellus hesperus} & 85 & 100 \\
			\\
			Family: Mormoopidae && \\
			13 \textit{Mormoops megalophylla} & 10 & 100 \\
			14 \textit{Pteronotus davyi} & 8 & 100 \\
			15 \textit{Pteronotus parnellii} & 23 & 100 \\
			16 \textit{Pteronotus personatus} & 7 & 51 \\
			\\
			Family:Phyllostomidae && \\
			17 \textit{Artibeus jamaicensis} & 11 & 82 \\
			18 \textit{Desmodus rotundus} & 6 & 38 \\
			19 \textit{Leptonycteris yerbabuenae} & 26 & 100 \\
			20 \textit{Macrotus californicus} & 6 & 53 \\
			21 \textit{Sturnira ludovici} & 8 & 51 \\
			22 \textit{Sturnira lilium} & 4 & 20 \\
			\botrule
		\end{tabular}
	}
	\begin{tabnote}
		$^{\text a}$Sample table footnote.
	\end{tabnote}
	\label{tab::dataset}
\end{table}

The 
The echolocation call dataset used for this study is the

\subsection{Recordings}

>>>>

The post processed echolocation call data accompanying Stathopoulos et al. \cite{stathopoulos2017bat} was used in this analysis. Echolocation calls were recorded across north and central Mexico with a Pettersson 1000x bat detector (Pettersson Elektronik AB, Uppsala, Sweden). Live trapped bats were measured and identified to species level using field keys.\cite{ceballos2005mamiferos} \cite{medellin2sanchez} Bats were recorded either while released from the hand or while tied to a zip line. The bat detector was set to record calls manually in real time, full spectrum at 500 kHz. 
In total the dataset consists of 22 species in five families, 449 individual bats and 1816 individual echolocation call recordings.

\begin{table}[ht]
	\tbl{Echolocation Call Dataset Statistics}
	{\begin{tabular}{@{}lccc@{}} \toprule
			Species & Key & Individuals & Calls \\ \colrule
			Family: Emballonuridae &&& \\
			1 \textit{Balantiopteryx plicata} & Bapl & 16 & 100 \\
			\\
			Family: Molossidae &&& \\
			2 \textit{Nyctinomops femorosaccus} & Nyfe & 16 & 100 \\
			3 \textit{Tadarida brasiliensis} & Tabr & 49 & 100  \\
			\\
			Family: Vespertilionidae &&& \\
			4 \textit{Antrozous pallidus} & Anpa & 58 & 100 \\
			5 \textit{Eptesicus fuscus} & Epfu & 74 & 100 \\
			6 \textit{Idionycteris phyllotis} & Idph & 6 & 100 \\
			7 \textit{Lasiurus blossevillii} & Labl & 10 & 90 \\
			8 \textit{Lasiurus cinereus} & Laci & 5 & 42 \\
			9 \textit{Lasiurus xanthinus} & Laxa & 8 & 100 \\
			10 \textit{Myotis volans} & Myvo & 8 & 100 \\
			11 \textit{Myotis yumanensis} & Myyu & 5 & 89 \\
			12 \textit{Pipistrellus hesperus} & Pihe & 85 & 100 \\
			\\
			Family: Mormoopidae &&& \\
			13 \textit{Mormoops megalophylla} & Mome & 10 & 100 \\
			14 \textit{Pteronotus davyi} & Ptda & 8 & 100 \\
			15 \textit{Pteronotus parnellii} & Ptpa & 23 & 100 \\
			16 \textit{Pteronotus personatus} & Ptpe & 7 & 51 \\
			\\
			Family:Phyllostomidae &&& \\
			17 \textit{Artibeus jamaicensis} & Arja & 11 & 82 \\
			18 \textit{Desmodus rotundus} & Dero & 6 & 38 \\
			19 \textit{Leptonycteris yerbabuenae} & Leye & 26 & 100 \\
			20 \textit{Macrotus californicus} & Maca & 6 & 53 \\
			21 \textit{Sturnira ludovici} & Stlu & 8 & 51 \\
			22 \textit{Sturnira lilium} & Stli & 4 & 20 \\
			\botrule
		\end{tabular}
	}
	\label{tab::dataset}
\end{table}

Phylogenetic relationships between species are described and dated according to the Bat super-tree produced by Collen.\cite{collen2012evolution}

\begin{figure}
	\centering
	\includegraphics[width= 0.9\textwidth]{../Figures/Phylogeny.eps}
\end{figure}
\subsection{Recordings}
